\documentclass[resmargin, centered, 11pt]{../res}
%Packages
	\usepackage{array,ragged2e} %Tabular formating
	\usepackage[pdfpagemode=FullScreen, colorlinks=true, linkcolor=black,  urlcolor=black]{hyperref} 
	\usepackage{fancyhdr}
	\usepackage[margin=1cm]{geometry}
	% allow hyphenation (was disabled)
	% \usepackage[none]{hyphenat} %To stop hyphenation
	\usepackage{enumitem}
	\usepackage{multicol}
	\usepackage{printlen} %for printing measurements
	\usepackage{xcolor}
	\usepackage{fontawesome5}  %For LinkedIn icon

%Dimensions, Settings & Variables
	\setlength{\columnseprule}{1pt} %For multicols
	\renewcommand{\familydefault}{\sfdefault}
	
%CuLi
	\def \fullwidth{\textwidth}
	\def \subwidth{13.5cm}
	\def \halfwidth{6.5cm}
	\def \titlewidth{4.25cm}

	\newcommand{\tab}[1][1cm]{\hspace*{#1}} 
	\newcommand{\loose}{\vspace{0.35cm}}
	\newcommand{\tight}{\vspace{-0.15cm}}
	\newcommand{\tighter}{\vspace{-0.5cm}}
	\newcommand{\subtext}[1]{\tab[0.5cm] \parbox{\dimexpr\fullwidth-0.5cm\relax}{#1}}
	\newcommand{\subtitle}[1]{\vspace{-1cm} ~ \newline  \emph{\subtext{#1}}}
	
\begin{document}
\name{
	KIRKWOOD P. DONAVIN
}
\targetPosition{Bike Mechanic}
\tagline{Passionate about the beautiful, human-powered machines called bicycles \& getting client butts back in the saddle}
\address{\href{mailto:kirkwood.donavin@gmail.com}{Kirkwood.Donavin@Gmail.com}}
\address{+1 (801) 554-6834}
\address{\linkedinbtn{https://www.linkedin.com/in/kirkwood-donavin}}
\address{\stravabtn{https://www.strava.com/athletes/2005740}}

\begin{resume}
    
\fullline

\section{Summary}

Experienced mechanic and community educator passionate about keeping people moving through human-powered (and e-powered!) transportation. Experienced in diagnosing and repairing everything from everyday commuter issues to complex drivetrain and brake systems, with a strong focus on safety, reliability, and rider confidence. Motivated by adventure and access, from daily commuting to long rides, bikepacking, and mountain exploration.

\fullline

\section{Experience}

\title{Mechanics Instructor}
\employer{Bicycle Collective}
\dates{May 2025 to Present}
\location{Salt Lake City, UT}
\begin{position}
	Instructor for the Bicycle Collective's community education program. Involved in course planning, as well as instruction or aiding co-instructors. 
	
	\bsc{Courses Offered:} Drivetrains, Brakes (rim \& rotor), Bearing Systems, Tubeless Tires, Wheels, Suspension Systems
\end{position}

\title{Volunteer Mechanic}
\employer{Bicycle Collective}
\dates{May 2018 to Present}
\location{Salt Lake City, UT}
\begin{position}
	Core volunteer mechanic for the Bicycle Collective, a non-profit organization that provides good-will bicycles to those in our community most in need, and open-shop for DIY repairs to the community. Responsibilities include diagnosing and repairing a wide range of issues on donated bicycles, from flat tires and brake adjustments to more complex drivetrain repairs. Mentoring other volunteers to ensure efficient workflow and high-quality service.
\end{position}

\title{SLC Shop Rep. to the Board}
\employer{Bicycle Collective}
\dates{June 2023 to Present}
\location{SL, UT}
\begin{position}
	\begin{itemize}
		\item \bsc{Shop Representative} Represent shop volunteers and staff on the Bicycle Collective Board of Directors, providing frontline feedback to guide organizational decisions.
		\item \bsc{Strategic Planning} Collaborate with other board members on strategic long-term planning; board-member / representative recruitment, especially from our organization's satellite communities (Ogden \& St. George); and Bicycle Prom, the Collective's annual fundraising event.
	\end{itemize}
\end{position}

\title{Mechanic}
\employer{Contender Bicycles/Sport's Den}
\dates{March 2018 to May 2018}
\location{SL, UT}
\begin{position}
	Junior mechanic for a high-volume shop specializing in road, gravel, and triathlon bikes. Responsibilities included diagnosing and repairing a wide range of bicycle issues, from brake adjustments \& bleeds, to more complex drivetrain repairs. Built high-end mountain bikes from the box.
\end{position}

\fullline

\section{EDUCATION}

\title{Course Highlights}
\employer{}
\dates{}
\location{}
\begin{position}
Outdoor Leadership, Wilderness First Aid, Rec. Avalance Safety I \& II (AAI)
\end{position}

\title{M.S. of Applied Economics}
\employer{Montana State University}
\dates{May 2015}
\location{Bozeman, MT}
\begin{position}
	\bsc{Thesis}: 
	\bref{https://www.slideshare.net/slideshow/embed\_code/key/K6qYsOYvj9u5Ab}{The Welfare Impacts of Engineers Without Borders in Western Kenya}
\end{position}

\title{B.A of International Relations}
\employer{Cornell College}
\dates{May 2011}
\location{Mount Vernon, IA}
\begin{position}
\end{position}

\end{resume}
\end{document}
